Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-26 xrb2/paper.tex
add some more figures
update refs

We use the Castro hydrodynamics code \citep{castro} and the simulation
framework introduced in \citet{flame_wave1}.  The main difference is
that we no longer boost the flames by adjusting the reaction rates and
conductivities.  By porting \castro\ to GPUs \citep{castro:sc20}, we
are able to run the unboosted flame simulations with fewer resources
than the boosted simulations used in our earlier paper.  For these
axisymmetric simulations, we adding a missing geometric source terms
from \citet{bernard-champmartin} that captures the effects of the
divergence of the flux operating on the azimuthal unit vector.  This
term is a small correction, but was missing from our earlier
simulations.

The initial model is setup in the same fashion as described in
\citet{flame_wave}.  In particular, we create a ``hot'' and ``cool''
hydrostatic model representing the ash and fuel states and blend the
two models laterally to create a hot region near the origin of
coordinates and a smooth transition to the cooler region at larger
radii.  In the calculations presented here, we explore the structure
of the initial models by varying some of the parameters, in particular, the temperature
of the neutron star and at the base of the fuel layer. \MarginPar{add plot showing models}

@@

>>>>

We use the Castro hydrodynamics code \citep{castro,castro_joss} and the simulation
framework introduced in \citet{flame_wave1}.  The main difference is
that we no longer boost the flames by adjusting the reaction rates and
conductivities.  By porting \castro\ to GPUs \citep{sc20_gpu}, we
are able to run the unboosted flame simulations with fewer resources
than the boosted simulations used in our earlier paper.  For these
axisymmetric simulations, we adding a missing geometric source terms
from \citet{bernard-champmartin} that captures the effects of the
divergence of the flux operating on the azimuthal unit vector.  This
term is a small correction, but was missing from our earlier
simulations.

The initial model is setup in the same fashion as described in
\citet{flame_wave}.  In particular, we create a ``hot'' and ``cool''
hydrostatic model representing the ash and fuel states and blend the
two models laterally to create a hot region near the origin of
coordinates and a smooth transition to the cooler region at larger
radii.  In the calculations presented here, we explore the structure
of the initial models by varying some of the parameters, in particular, the temperature
of the neutron star and at the base of the fuel layer.

\begin{figure}[t]
\centering
\plotone{hot}
\caption{\label{fig:hot_profiles} Initial temperature and density structure vs.\ height in the ``hot'' state.}
\end{figure}

\begin{figure}[t]
\centering
\plotone{cold}
\caption{\label{fig:cold_profiles} Initial temperature and density structure vs.\ height in the ``cool'' state.}
\end{figure}

@@

Next steps: 3-d, explore resolution more, H/He flames, MHD flames
